Should I Airbnb My Property?

### 2017-03-04 abb_Writeup.Rmd
host classificatoin, p1

<!-- Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).  Short term revenues range from neglible to highs of greater than \$80,000.  While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not. Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing. -->

@@

  stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
  stre$tenure <- 'short-term extrapolated   '
  names(stre)[2] <- 'revenue'
  strp <- str.data[,c('bedrooms', 'str.pot.revenue')]
  strp$tenure <- 'short-term potential   '
  names(strp)[2] <- 'revenue'
  ltrr <- ltr.data[,c('bedrooms', 'gross.revenue')]
  ltrr$tenure <- 'long-term   '
  names(ltrr)[2] <- 'revenue'
  allr <- rbind(stre, strp, ltrr)

@@

```
```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE}

  #host.block.freq <- 
  ggplot(str.data, aes(x=block.rate)) + 
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

@@

  #block.rate.period <- 
ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

#host.type <-

ggplot(str.data, 
       aes(x=block.rate, y=blockpertime, color=host.type)) + 
  geom_point(alpha=.5, size=.8, shape=16) +
  ylab('Number of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

    scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +

  scale_color_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9])) + 
  theme(legend.position='bottom',
          legend.title = element_blank(),
        plot.title = element_text(hjust = 0.5))+
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1)))

@@

>>>>

Below we chart the distribution of the Extrapolated ($REV_e$) and Potential ($REV_p$) Short Term revenues against a distribution of the oserved long term revenues for the long term properties. Revenues from the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 8).  Extrapolated short term revenues range from neglible to highs of greater than \$80,000, with many of the properties showing very limited (less than \$10,000) revenue. The range of the distribution for the Potential Short Term revenue is similar, however, the distribution itself is much flatter, with many more properties showing potential incomes in the \$20,000 to \$40,000 range.

While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not.  When looking at potential revenues, however, a great deal more may have the potential to produce more revenue.  The high number of very low yield Airbnb properties in the Extrapoted condition suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing^[Do note that we have not considered any overall market demand issues when analyzing potential revenue.].

@@

  stre <- str.data[,c('bedrooms', 'str.ext.revenue')]
  stre$tenure <- 'short-term extrapolated   '
  names(stre)[2] <- 'revenue'
  strp <- str.data[,c('bedrooms', 'str.pot.revenue')]
  strp$tenure <- 'short-term potential   '
  names(strp)[2] <- 'revenue'
  ltrr <- ltr.data[,c('bedrooms', 'ltr.revenue')]
  ltrr$tenure <- 'long-term   '
  names(ltrr)[2] <- 'revenue'
  allr <- rbind(stre, strp, ltrr)

@@

#### Classifying Hosts

As the difference between extrapolated and potential revenue suggests, many short-term hosts are not listing their properties full-time.  There may be, therefore, different types of hosts operating in the Airbnb market. from anecdotal evidence, there are at least two types of hosts in the market: 1) Those that lease out their properties all the time in the name of profit maximization (Profit Seekers); and 2) Those that lease out their property when very infrequently, for example when they are away on vacation (Opportunistic Sharers).
If these are the dominant two forms of hosts in the market, then a distribution of properties by the percent of time which they are blocked shoudl be very bi-modal with profit seekers on the left and opportunistic sharers on the right. The left hand panel of figure 9 shows that this breakdown hold somewhat, with peaks of hosts at each end, but that there are also a considerable number of hosts who block their properties some of the time.  
There is also a third potential host type, that of the host who utilizies multiple platforms to list their short-term property.

@@

  host.block.freq <- ggplot(str.data, aes(x=block.rate)) + 
  geom_density(fill=str.col, color=str.col) +
  ylab('Frequency\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0,1,.2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Host Block Rate Frequency\n') +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
```

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=3.5}

  block.rate.period <- ggplot(str.data, aes(x=block.rate, y=nbr.block*extr.par)) + 
  geom_point(fill=str.col, color=str.col, size=.2) +
  ylab('Nbr of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
  scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

ggMultiPlots(host.block.freq, block.rate.period, cols=2)

@@

base.host <- ggplot(str.data, 
                    aes(x=block.rate, y=blockpertime)) + 
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') + 
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%', 
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4], 
                #                            abb.col[7], abb.col[9])) + 
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,
                                                                 alpha=1)))

ps.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Profit Seeker', ], size=.4)  +
  ggtitle('Profit Seekers')
os.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Opportunistic Sharer', ], 
             size=.4)  +
  ggtitle('Opportunistic Sharer')
mu.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Multi-Platform User', ], 
             size=.4)  +
  ggtitle('Multi-Platform User')
un.host <- base.host + 
  geom_point(data=str.data[str.data$host.type == 'Unknown', ], size=.4)  +
  ggtitle('Unknown')

ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)

@@

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, fig.height=4}

host.type.bar <- ggplot(str.data, aes(host.type, fill=host.type)) +
  geom_bar() +
  scale_fill_manual(values=c(abb.col[2], abb.col[4], abb.col[7], abb.col[9]))+
  theme(legend.position='none') +
  ylab('Frequency\n') + 
  xlab('\nHost Type') +
  ggtitle('Short Term Host Types') + 
  theme(plot.title = element_text(hjust = 0.5))

host.type.bar
```
